Finite Property Convex Elicitation Notes

### 2019-01-21 raf-notes.tex
start potential paper outline
minor edits

We will most often use this definition as follows.
Given a finite property $\Gamma : \P \toto \{1,\ldots,k\}$, we will seek some convex loss function $L : \reals^d \to \reals^\Y$ and a set of points $\X=\{x_1,\ldots,x_k\} \subset \reals^d$ such that the map $\varphi:i\mapsto x_i$ exhibits the essential elicitability of $\Gamma$.
In particular, using the set-valued link function $\psi:A\mapsto \varphi^{-1}(A\cap\X)$, we will have $\Gamma = \psi \circ \Gamma_L$, so that $\Gamma$ will be indirectly convex elicitable.

@@

We begin with a fairly trivial restatement of the definition of embeddability.
\begin{proposition}
  A finite property $\Gamma:\R\toto\P$ is $d$-embeddable if and only if there exists an embedding $\varphi: \R \to \reals^d$ and polytopes $T(r,y) \subseteq \reals^d$ for all $r\in\R, y\in\Y$, such that the following two conditions hold:
  \begin{enumerate}
  \item For all $r\in\R, p\in\P$, we have $r\in \Gamma(p) \iff 0 \in \sum_{y\in\Y} p_y T(r,y)$, where summation is the Minkowski sum.
  \item For all $y\in\Y$ there exists some convex function $L_y$ such that for all $r\in\R$ we have $T(r,y) = \partial L_y(r)$.
  \end{enumerate}
\end{proposition}
\begin{proof}
  If $\Gamma$ is $d$-embeddable, we have a convex loss $L$ such that
  \begin{align*}
    r \in \Gamma(p) &\iff \varphi(r) \in \argmin_{r'\in\reals^d} \E_p L(r',Y)\\
                    &\iff 0 \in \partial \E_p L(\varphi(r),Y) \\
                    &\iff 0 \in \sum_y p_y \partial L(\varphi(r),y)~.
  \end{align*}
  Thus, taking $T(r,y) = \partial L(r,y)$ satisfies (1) and trivially (2) with $L_y = L(\cdot,y)$.
  For the converse, we simply take $L(r,y) = L_y(r)$; by condition (1) and the argument above we have exactly that $L$ essentially elicits $\Gamma$.
  \raf{I just realized: we need to justify why we can assume $L$ has polytopical subgradients, vs just polyhedral.  I think this is equivalent to $L$ being finite on all of $\reals^d$, which we can assume, but will probably need machinery from the first part.}
\end{proof}

>>>>

We will most often use this definition as follows.
Given a finite property $\Gamma : \P \toto \{1,\ldots,k\}$, we will seek some convex loss function $L : \reals^d \to \reals^\Y$ and a set of points $\X=\{x_1,\ldots,x_k\} \subset \reals^d$ such that the map $\varphi:i\mapsto x_i$ exhibits the essential elicitability of $\Gamma$.
\raf{WARNING: I think the following is not true actually.  We need the weaker notion of a link function: given some $L$-optimal report in $\reals^d$, give me (at least) one optimal report according to $\Gamma$.}
In particular, using the set-valued link function $\psi:A\mapsto \varphi^{-1}(A\cap\X)$, we will have $\Gamma = \psi \circ \Gamma_L$, so that $\Gamma$ will be indirectly convex elicitable.

@@

We begin with a fairly trivial restatement of the definition of embeddability.
\begin{proposition}
  A finite property $\Gamma:\R\toto\P$ is $d$-embeddable if and only if there exists an embedding $\varphi: \R \to \reals^d$ and polytopes $T(r,y) \subseteq \reals^d$ for all $r\in\R, y\in\Y$, such that the following two conditions hold:
  \begin{enumerate}
  \item For all $r\in\R, p\in\P$, we have $r\in \Gamma(p) \iff 0 \in \sum_{y\in\Y} p_y T(r,y)$, where summation is the Minkowski sum.
  \item For all $y\in\Y$ there exists some convex function $L_y$ such that for all $r\in\R$ we have $T(r,y) = \partial L_y(\varphi(r))$.
  \end{enumerate}
\end{proposition}
\begin{proof}
  If $\Gamma$ is $d$-embeddable, we have a convex loss $L$ such that
  \begin{align*}
    r \in \Gamma(p) &\iff \varphi(r) \in \argmin_{r'\in\reals^d} \E_p L(r',Y)\\
                    &\iff 0 \in \partial \E_p L(\varphi(r),Y) \\
                    &\iff 0 \in \sum_y p_y \partial L(\varphi(r),y)~.
  \end{align*}
  Thus, taking $T(r,y) = \partial L(r,y)$ satisfies (1) and trivially (2) with $L_y = L(\cdot,y)$.
  For the converse, we simply take $L(r,y) = L_y(r)$; by condition (1) and the argument above we have exactly that $L$ essentially elicits $\Gamma$.
  \raf{I just realized: we need to justify why we can assume $L$ has polytopical subgradients, vs just polyhedral.  I think this is equivalent to $L$ being finite on all of $\reals^d$, which we can assume, but will probably need machinery from the first part.}
\end{proof}
